Add N_tilde to the data_2nd_stage (<span style='color:blue'>Score: /10 </span>)

### 2025-08-14 codes/R/CF_Continuous_Loop_new.Rmd
Initial commit to CF_Continuous repo

## Packages and functions
```{r}
#--- packages ---#
library(tidyverse)
library(data.table)
library(mgcv)
library(spatialsample)
library(parallel)
library(sf)
library(grf)
library(ranger)
library(xgboost)
library(mgcv)
# library(here)
library(reticulate)
library(readr)
library(dplyr)
library(tidyr)

@@

#--- python functions ---#
use_condaenv("cf_conda311", required = TRUE)
py_config()
py_run_string("from econml.dml import CausalForestDML; print('CausalForestDML imported OK')")
source_python("/Users/mmousavi2/Dropbox/Causal_climate/My_own_Shared/Causal-ML-continuous-treatment/codes/Python/run_CF_c.py")
```

```{r}
# project‐root path:
proj_root <- "/Users/mmousavi2/Dropbox/Causal_climate/Data_and_results_CF_Continuous"

# “.here” file
here_file <- file.path(proj_root, ".here")
if (!file.exists(here_file)) {
  message("Creating .here in ", proj_root)
  file.create(here_file)
}

```

@@

```{r}
# turn off multi-threading
Sys.setenv(OMP_NUM_THREADS = 1, MKL_NUM_THREADS = 1)

# load data only once, then drop
library(here)
raw_sim_data <- readRDS(here("data", "raw_sim_data.rds"))
rm(list = setdiff(ls(), c("raw_sim_data", "np", "run_CF_c_py", "gm_wrapper_functions_you_need")))
gc()
```

@@

# how many fields to train on?
n_fields <- 1

@@

# the right split file under <project_root>/data/train_test_split
splits_file <- here(
  "data", "train_test_split",
  sprintf("train_test_splits_%dfields.csv", n_fields)
)
output_dir <- here(
  "results",
  sprintf("CF_outcome_%d_fields", n_fields)
)
if (!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)

@@

@@

x_vars    <- c("Nk", "plateau", "b0")
#T_formula <- yield ~ s(N, k = 4)
T_formula <- y_tilde ~ s(N, k = 4)
# cf_results <- lapply(train_test_splits$test_id, function(test_sim_id)
cf_results <- lapply(train_test_splits$test_id, function(test_sim_id) {
  result_file <- file.path(output_dir, paste0("sim_", test_sim_id, ".rds"))
  if (file.exists(result_file)) {
    message(sprintf("Skipping sim %d (already saved)", test_sim_id))
    return(NULL)
  }

@@

  }, error = function(e) {
    message(sprintf("Error with sim %d: %s", test_sim_id, e$message))
    data.table(
      sim        = test_sim_id,
      aunit_id   = integer(),
      opt_N_hat  = numeric(),
      opt_N      = numeric()
    )
  })
})
```

>>>>

## Packages and functions
```{r}
#--- packages ---#
library(tidyverse)
library(data.table)
library(mgcv)
library(spatialsample)
library(parallel)
library(sf)
library(grf)
library(ranger)
library(xgboost)
library(mgcv)
#library(here)
#library(reticulate)
library(readr)
library(dplyr)
library(tidyr)

Sys.setenv(
  OMP_NUM_THREADS = "1",
  OPENBLAS_NUM_THREADS = "1",
  MKL_NUM_THREADS = "1",
  VECLIB_MAXIMUM_THREADS = "1"  # macOS Accelerate safeguard
)

library(reticulate)
use_condaenv("cf_conda311", required = TRUE)
py_config()

py_run_string("import sys, os; sys.path.append('/Users/mmousavi2/Dropbox/Causal_climate/My_own_Shared/Causal-ML-continuous-treatment/codes/Python')")

# clear any stale bytecode that might have been written under a different toolchain
system("find /Users/mmousavi2/Dropbox/Causal_climate/My_own_Shared/Causal-ML-continuous-treatment/codes/Python -name '__pycache__' -type d -prune -exec rm -rf {} +")

# now import without executing R helpers:
py_run_string("import run_CF_c; print('run_CF_c imported OK; has run_CF_c_py:', hasattr(run_CF_c, 'run_CF_c_py'))")

#--- python functions ---#
# use_condaenv("cf_conda311", required = TRUE)
# py_config()
# py_run_string("from econml.dml import CausalForestDML; print('CausalForestDML imported OK')")
source_python("/Users/mmousavi2/Dropbox/Causal_climate/My_own_Shared/Causal-ML-continuous-treatment/codes/Python/run_CF_c.py")

@@

#--- python functions ---#
use_condaenv("cf_conda311", required = TRUE)
py_config()
py_run_string("from econml.dml import CausalForestDML; print('CausalForestDML imported OK')")
source_python("/Users/mmousavi2/Dropbox/Causal_climate/My_own_Shared/Causal-ML-continuous-treatment/codes/Python/run_CF_c.py")
```
```{r setup, include=FALSE}
# project‐root path:
proj_root <- "/Users/mmousavi2/Dropbox/Causal_climate/Data_and_results_CF_Continuous"

# ensure a `.here` exists at the project root (optional)
here_file <- file.path(proj_root, ".here")
if (!file.exists(here_file)) file.create(here_file)

# turn off multi-threading
Sys.setenv(OMP_NUM_THREADS = 1, MKL_NUM_THREADS = 1)

# load here (no need to set root—see next chunk)
library(here)
```

@@

```{r}
# Data (use here() with absolute root to avoid any cached project root)
rds_path <- here(proj_root, "data", "raw_sim_data.rds")
if (!file.exists(rds_path)) stop("File not found: ", rds_path)

raw_sim_data <- readRDS(rds_path)

# keep memory tidy
rm(list = setdiff(ls(), c("raw_sim_data", "np", "run_CF_c_py", "gm_wrapper_functions_you_need", "proj_root")))
gc()
```

@@

# how many fields to train on?
n_fields <- 10

@@

# the right split file under <project_root>/data/train_test_split
proj_root <- "/Users/mmousavi2/Dropbox/Causal_climate/Data_and_results_CF_Continuous"

splits_file <- here(
  proj_root,
  "data", "train_test_split",
  sprintf("train_test_splits_%dfields.csv", n_fields)
)

output_dir <- file.path(
  "/Users/mmousavi2/Desktop/tes_one_loop",
  sprintf("CF_outcome_%d_fields", n_fields)
)
if (!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)

@@

#train_test_splits <- train_test_splits_10fields

@@

x_vars    <- c("Nk", "plateau", "b0")
#T_formula <- yield ~ s(N, k = 4)
T_formula <- y_tilde ~ s(N, k = 4)
# cf_results <- lapply(train_test_splits$test_id, function(test_sim_id)
cf_results <- lapply(train_test_splits$test_id[1], function(test_sim_id) {
  result_file <- file.path(output_dir, paste0("sim_", test_sim_id, ".rds"))
  if (file.exists(result_file)) {
    message(sprintf("Skipping sim %d (already saved)", test_sim_id))
    return(NULL)
  }

@@

  }, error = function(e) {
    message(sprintf("Error with sim %d: %s", test_sim_id, e$message))
    data.table(
      sim        = test_sim_id,
      aunit_id   = integer(),
      opt_N_hat  = numeric(),
      opt_N      = numeric()
    )
  })
})
```
# rmse

```{r}
rmse_1_fields_one_loop <- sqrt(mean((sim_001_eonr$opt_N_hat - sim_001_eonr$opt_N)^2, na.rm = TRUE))  
rmse_1_fields_one_loop
```

### 2025-08-14 codes/R/CF_loop.Rmd
CF loop still needs attention to make it organaized
Initial commit to CF_Continuous repo

source_python("/Users/monamousavi/Dropbox/Causal_climate/My_own_Shared/Causal-ML-continuous-treatment/codes/Python/run_CF_c.py")

```

# CF

```{r}

## ───────────────────────────────────────
train_test_splits <- train_test_splits_1fields
n_fields <- 1  # how many train sims

@@

## ─  keep an in-memory list ────────────
#cf_all_results <- vector("list", length = nrow(train_test_splits))
#names(cf_all_results) <- train_test_splits$test_id
train_test_splits <- subset(train_test_splits, !test_id %in% as.integer(sub("^sim_(\\d+)\\.rds$","\\1", basename(list.files(path.expand(output_dir), "^sim_\\d+\\.rds$")))))

## ── Loop over test sims ───────────────────────────────────────────────────────
for (i in seq_len(nrow(train_test_splits))) {

  test_sim_id <- train_test_splits$test_id[i]
  out_fn <- file.path(output_dir, sprintf("sim_%03d.rds", as.integer(test_sim_id)))

@@

  # 
  tryCatch({

    ## 1) Train/test IDs
    split_row     <- train_test_splits[i, ]
    train_sim_ids <- as.integer(unlist(split_row[paste0("train_", 1:n_fields)]))
    sim_id_ls     <- c(train_sim_ids, test_sim_id)

@@

    #  keep in memory too
    #cf_all_results[[as.character(test_sim_id)]] <- res

@@

    message("Finished sim ", test_sim_id, " → ", basename(out_fn),
            " (corr = ", round(corr_val, 3), ")")

    # Free RAM periodically
    rm(res, te_hat_cf, te_info, response_data, train_data, test_data)
    if (i %% 10 == 0) gc()

  }, error = function(e) {
    message("ERROR in sim ", test_sim_id, ": ", conditionMessage(e))
    #  which sim failed
    err_row <- data.frame(
      test_sim_id = test_sim_id,
      error       = conditionMessage(e),
      ts          = as.character(Sys.time())
    )
    write.table(
      err_row,
      file      = file.path(output_dir, "errors.csv"),
      sep       = ",",
      row.names = FALSE,
      col.names = !file.exists(file.path(output_dir, "errors.csv")),
      append    = TRUE
    )
  })

}

## ── save the whole list at the end ─────────────────────────────────
# saveRDS(cf_all_results, file.path(output_dir, "_all_results.rds"))

```
# read in

@@

  # optional CSV
  #fwrite(e, sub("\\.rds$", ".csv", fn_rds))

  rm(r, e)
  if (i %% 50 == 0) gc()
}

```

>>>>

source_python("/Users/monamousavi/Dropbox/Causal_climate/My_own_Shared/Causal-ML-continuous-treatment/codes/Python/run_CF_c.py")
```

# CF loop

```{r}
## ───────────────────────────────────────
train_test_splits <- train_test_splits_1fields
n_fields <- 1 # how many train sims

@@

## ─  keep an in-memory list ────────────
# cf_all_results <- vector("list", length = nrow(train_test_splits))
# names(cf_all_results) <- train_test_splits$test_id
train_test_splits <- subset(train_test_splits, !test_id %in% as.integer(sub("^sim_(\\d+)\\.rds$", "\\1", basename(list.files(path.expand(output_dir), "^sim_\\d+\\.rds$")))))

## ── Loop over test sims ───────────────────────────────────────────────────────
for (i in seq_len(nrow(train_test_splits))) {
  test_sim_id <- train_test_splits$test_id[i]
  out_fn <- file.path(output_dir, sprintf("sim_%03d.rds", as.integer(test_sim_id)))

@@

  #
  tryCatch(
    {
      ## 1) Train/test IDs
      split_row <- train_test_splits[i, ]
      train_sim_ids <- as.integer(unlist(split_row[paste0("train_", 1:n_fields)]))
      sim_id_ls <- c(train_sim_ids, test_sim_id)

@@

      #  keep in memory too
      # cf_all_results[[as.character(test_sim_id)]] <- res

@@

      message(
        "Finished sim ", test_sim_id, " → ", basename(out_fn),
        " (corr = ", round(corr_val, 3), ")"
      )

      # Free RAM periodically
      rm(res, te_hat_cf, te_info, response_data, train_data, test_data)
      if (i %% 10 == 0) gc()
    },
    error = function(e) {
      message("ERROR in sim ", test_sim_id, ": ", conditionMessage(e))
      #  which sim failed
      err_row <- data.frame(
        test_sim_id = test_sim_id,
        error       = conditionMessage(e),
        ts          = as.character(Sys.time())
      )
      write.table(
        err_row,
        file      = file.path(output_dir, "errors.csv"),
        sep       = ",",
        row.names = FALSE,
        col.names = !file.exists(file.path(output_dir, "errors.csv")),
        append    = TRUE
      )
    }
  )
}

## ── save the whole list at the end ─────────────────────────────────
# saveRDS(cf_all_results, file.path(output_dir, "_all_results.rds"))
```

# read in

@@

  # optional CSV
  # fwrite(e, sub("\\.rds$", ".csv", fn_rds))

  rm(r, e)
  if (i %% 50 == 0) gc()
}
```
